### 2017-05-09 paper/intro.tex
pass on abstract and intro

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workload.  Evidence of this are the
Google TAP system~\cite{google-tap,google-ci} and the Microsoft
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficiently build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.  This paper reports on an
empirical study we conducted to analyze the usage and impact of
low-level parallelization in speeding up testing for open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.

@@

The dimensions of analysis we considered in this study are as follows:
potential, effectiveness, adoption, and tradeoffs.  Each dimension
focuses on one aspect of our study.  The dimension \textbf{potential}
measures the potential of parallelization to reduce testing costs.  In
the limit, parallelization would be fruitless if all projects used
short-running test suites or if the bulk of execution cost was
dominated by a single test in the suite.  The dimension
\textbf{effectiveness} measures the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} on testing costs.  Intuitively, benefits are
proportional to the cost reduction that parallelization brings.  In
the limit, however, the overhead of spawning virtual machines or
threads can even result in added cost.  The dimension
\textbf{adoption} evaluates (i) how often open-source projects use
parallelization schemes and (ii) how developers involved in costly
projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance to the technology
and its reasons.  Finally, the dimension \textbf{tradeoffs} evaluates
the issues and benefits associated with\Comment{running test suites
  with} different parallel configurations.  Note that the
configuration choice can affect both test cost and test flakiness,
which is caused by the non-determinism resulted from running test
methods and classes in different orderings.

@@

\subsection{Summary of ``Potential'' results}

We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  Results indicate that nearly
\percentMedLongRunning{} of the projects take at least 1m to run their
test suites and \percentLongRunning{} of the projects take at least 5m
to run their suites.  Considering the \numMedLong{} projects in those
two groups, the average execution time is \averageMedLongRunning{}.
Results also show that individual tests are typically short-running,
taking often less than half a second to run.  Furthermore, we found
that only in rare cases few test cases monopolize execution cost
associated with each test suite.  \emph{Overall, our results suggest
  that test suite parallelization has the potential to optimize test
  suites.}

\subsection{Summary of ``Effectiveness'' results}

As to avoid introduction of unintended noise when measuring time, we
evaluated effectiveness on projects that we knew a priori ran their
test suite in parallel by default.  Results indicate that the average
speedup of parallelization was \avgSpeedup{}x.  Although we found
cases with very high speedups (\eg{}, 9.2x), we found some cases where
speedups were insignificant.  \emph{Overall, our results suggest that
  it may not be obvious to achieve huge speedups with test suite
  parallelization.}

\subsection{Summary of ``Adoption'' results}

We considered two aspects in measuring adoption of the technology.
First, we analyzed quantitatively current usage of parallelism in
open-source projects.  Then, we investigated the key reasons that
justify resistance of developers in using test suite parallelization.
For the quantitative analysis we checked both statically (parsing
build files) and dynamically (monitoring execution of build files) for
the presence of parallelization.  Considering only those projects that
take longer than a minute to run their test suites, we found that only
\percentParallel{} of them use parallelism.  When considering the
feedback received from developers involved in those projects we
realized the proportion should was a bit higher, of
\percentParallelUpdated{}, but still relatively low.  For the
qualitative analysis we surveyed developers from a selection of costly
projects that did not use parallelization.  Section~\ref{sec:rqE}
details our selection methodology. \emph{Results indicate that dealing
  with concurrency issues related with parallelization (in particular,
  the extra work to organize test suite to safely explore concurrency)
  was the main barrier for adoption.  Other reasons included
  availability of continuous integration services and unfamiliarity
  with the technology.}

@@

\subsection{Summary of ``Tradeoff'' results}

\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla bla}

>>>>

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workload.  Evidence of this are the
Google TAP system~\cite{google-tap,google-ci} and the Microsoft
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficiently build massive
amounts of code and run tests.  Building in-house server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the test suite fo the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or inexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization in speeding up testing
in open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research~\cite{yoo-harman-stvr2012}.  Note that
parallelization is complementary to other approaches to mitigate
testing costs such as (safe) test
selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.  The dimensions of
analysis we considered in this study are (i) potential, (iii)
adoption, and (iii) tradeoffs, (iv) speedups.

%% Each dimension
%% focuses on one aspect of the study.

The dimension \textbf{feasibility} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects used short-running
test suites or if the bulk of execution cost was dominated by a single
test in the suite.  The dimension \textbf{adoption} evaluates (i) how
often existing open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance of practicioners to the technology and to understand their
reasons.  The dimension \textbf{tradeoffs} evaluates the issues and
benefits associated with\Comment{running test suites with} the use of
possible parallel configurations.  Note that the configuration choice
affects testing cost and flakiness, caused by the non-determinism
resulted from running different schedulings of test methods and
classes.  Finally, the dimension \textbf{speedups} measures the
observed impact of parallelization\Comment{~---~when used in selected
  open-source projects~---~} in running times.  We briefly summarize
each of these dimensions in the following.

@@

\vspace{1ex}\noindent\textbf{Feasibility.}~
We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  Results indicate that nearly
\percentMedLongRunning{} of the projects take at least 1m to run their
test suites and \percentLongRunning{} of the projects take at least 5m
to run their suites.  Considering the \numMedLong{} projects in those
two groups, the average execution time is \averageMedLongRunning{}.
Results also show that individual tests are typically short-running,
taking often less than half a second to run.  Furthermore, we found
that only in rare cases few test cases monopolize execution cost
associated with each test suite.  \emph{Overall, our results suggest
  that test suite parallelization has the potential to optimize test
  suites.}

\vspace{1ex}\noindent\textbf{Adoption.}~ We considered two aspects in
measuring technology adoption.  First, we measured usage of
parallelism in open-source projects.  Then, we ran a survey with
developers to understand the reasons that explain resistance to using
the technology.  For the quantitative analysis we checked both
statically (parsing build files) and dynamically (monitoring execution
of build files) for the presence of parallelization.  Considering only
those projects that take longer than a minute to run their test
suites, we found that only \percentParallel{} of them use parallelism.
When correcting this value with the feedback obtained a posteriori
from developers, we realized that the proportion should be higher, of
\percentParallelUpdated{}.  For the qualitative analysis we surveyed
developers from a selection of costly projects that did not use
parallelization.  \emph{Results indicate that test suite
  parallelization is underutilized and dealing with concurrency issues
  related with parallelization (\eg{}, the extra work to organize test
  suite to avoid concurrency errors) was the main barrier for
  adoption.  Other reasons included availability of continuous
  integration services and unfamiliarity with the technology.}

@@

\vspace{1ex}\noindent\textbf{Tradeoffs.}~
\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla bla}

\vspace{1ex}\noindent\textbf{Speedups.}~
%% \Mar{move to here} Intuitively, benefits are
%% proportional to the cost reduction that parallelization brings.  In
%% the limit, however, the overhead of spawning virtual machines or
%% threads can even result in added cost.
\Mar{...revise with scalability results...}
As to avoid introduction of unintended noise when measuring time, we
evaluated effectiveness on projects that we knew a priori ran their
test suite in parallel by default.  Results indicate that the average
speedup of parallelization was \avgSpeedup{}x.  Although we found
cases with very high speedups (\eg{}, 9.2x), we found some cases where
speedups were insignificant.  \emph{Overall, our results suggest that
  it may not be obvious to achieve huge speedups with test suite
  parallelization.}

\Mar{write one or two lessons learned}
